An Open-Source OpenSim Oculomotor Model for Kinematics and Dynamics Simulation

### 2018-07-10 doc/manuscript.tex
update text

Rapid and accurate eye movements are crucial for coordinated direction of
gaze. Studying human eye movement has significant implications for improving our
understanding of the oculomotor system and treating visuomotor disorders. Over
the past decades, biomechanics simulation has provided the means to analyze
different human movements. The same principles can be used to analyze visual
tasks by modeling the musculoskeletal properties of the oculomotor
system. Consequently, this model can be used to investigate muscle activation
patterns during static fixation, analyze the dynamics of various eye movements,
calculate metabolic costs and simulate different eye disorders, such as
different forms of strabismus. Furthermore, it can be easily integrated with
available full body models in order to analyze the relation between the
vestibular and oculomotor systems.

Eye movements are a generated from a coordination of the six \gls{em}. Clinical
trials have provided a profound knowledge of how the \gls{em} act on the eye
globe, the resistive tension of the surrounding tissues and the length-tension
relationship of the muscles. Various computational models of the extraocular
muscles and orbital mechanics have been proposed, which provide insight and
scientific bases for oculomotor biomechanics, control of eye movement and
binocular misalignment. These models focus on the realism of muscle behavior and
they were based on the viscoelastic properties and physiological data \gls{em}.

The first 3D biomechanical model was developed by~\cite{Robinson1964a,
  Robinson1969}, who simplified the formulation by considering the elasticity of
the \gls{em} ignoring their dynamics. The model incorporates anatomically
realistic muscle paths and empirical innervation-length-tension
relationships. To study the neural control of rapid saccadic movements, models
using anatomical and mechanical properties of \gls{em} have been developed by
accounting for the nonlinear muscle dynamics~\cite{Thelen2003a,
  Millard2013}. Such models, having the advantage of supporting dynamics
simulation, are used in conjunction with brain level controllers \hl{seb}.

@@

\begin{equation}\label{equ:passive-tissue}
  \vec{f}_t = -k_p \vec{q} - k_c 10^{-3} \vec{q}^3 - k_d * \vec{\dot{q}}
\end{equation}
% 
where, $\vec{f}_t$ represents the passive tissue forces, $k_p= 0.002225$ N m /
rad, $k_c= 34.5297$ N m / (rad\textsuperscript{3}) and $k_v= 0.002$ N m s / rad
the constants and $\vec{\dot{q}} \inr{3}$ the rotational coordinates of the
model. These forces serve the eye’s stabilization, and are modeled using
\texttt{OpenSim}'s expression based coordinate force.

@@

A realistic oculomotor model representing the motility of a normal human eye was
presented and made publicly available. The parameters of the model were
calibrated using available experimental measured data. The model can be used for
kinematics and dynamics analysis or as a tool for obtaining the muscle
activations that generate a desired saccade, using a closed-loop fixation
controller in a \gls{fd} manner. There is of course space for further
improvement, which will enhance the accuracy and the predictability of the
proposed computational eye model. In this study, we didn't attempt to model the
muscle pulleys, which vary as a function of the model coordinates. Furthermore,
the users should consider validation of the eye model based on the requirements
of the targeted utility of the model and the variables of interests.

@@

\bibliography*{mylibrary}
\addcontentsline{toc}{chapter}{Bibliography}

>>>>

Rapid and accurate eye movements are crucial for coordinated direction of
gaze~\cite{Lee2006}. Studying human eye movement has significant implications
for improving our understanding of the oculomotor system and treating visuomotor
disorders. Over the past decades, biomechanics simulation has provided the means
to analyze different human movements. The same principles can be used to analyze
visual tasks by modeling the musculoskeletal properties of the oculomotor
system. Consequently, this model can be used to investigate muscle activation
patterns during static fixation, analyze the dynamics of various eye movements,
calculate metabolic costs and simulate different eye disorders, such as
different forms of strabismus. Furthermore, it can be easily integrated with
available full body models in order to analyze the relation between the
vestibular and oculomotor systems.

Eye movements are a generated from a coordination of the six \gls{em}. Clinical
trials have provided a profound knowledge of how the \gls{em} act on the eye
globe~\cite{Robinson1969a}, the resistive tension of the surrounding tissues and
the length-tension relationship of the muscles~\cite{Collins1981}. Various
computational models of the extraocular muscles and orbital mechanics have been
proposed, which provide insight and scientific bases for oculomotor
biomechanics, control of eye movement and binocular misalignment. These models
focus on the realism of muscle behavior and they were based on the viscoelastic
properties and physiological data \gls{em}.

The first 3D biomechanical model was developed by~\cite{Robinson1964a,
  Robinson1969}, who simplified the formulation by considering the elasticity of
the \gls{em} ignoring their dynamics. The model incorporates anatomically
realistic muscle paths and empirical innervation-length-tension
relationships. To study the neural control of rapid saccadic movements, models
using anatomical and mechanical properties of \gls{em} have been developed by
accounting for the nonlinear muscle dynamics~\cite{Thelen2003a,
  Millard2013}. Such models, having the advantage of supporting dynamics
simulation, are used in conjunction with brain level
controllers~\cite{James2018}.

@@

\begin{equation}\label{equ:passive-tissue}
  \vec{f}_t = -k_p \vec{q} - k_c 10^{-3} \vec{q}^3 - k_d * \vec{\dot{q}}
\end{equation}
% 
where, $\vec{f}_t$ represents the passive tissue forces, $k_p= 0.002225$ N m /
rad, $k_c= 34.5297$ N m / (rad\textsuperscript{3}) and $k_v= 0.002$ N m s / rad
the constants and $\vec{\dot{q}} \inr{3}$ the rotational coordinates of the
model~\cite{Collins1981}. These forces serve the eye’s stabilization, and are
modeled using \texttt{OpenSim}'s expression based coordinate force.

@@

A realistic oculomotor model representing the motility of a normal human eye was
presented and made publicly available. The parameters of the model were
calibrated using available experimental measured data. The model can be used for
kinematics and dynamics analysis or as a tool for obtaining the muscle
activations that generate a desired saccade, using a closed-loop fixation
controller in a \gls{fd} manner. There is of course space for further
improvement, which will enhance the accuracy and the predictability of the
proposed computational eye model. In this study, we didn't attempt to model the
muscle pulleys~\cite{Kono2002a}, which vary as a function of the model
coordinates. Furthermore, the users should consider validation of the eye model
based on the requirements of the targeted utility of the model and the variables
of interests.

@@

\bibliography{mylibrary}
\addcontentsline{toc}{chapter}{Bibliography}
